### 2016-10-26 doc/publications/plos16/plos16.tex
add TCGA subsubsection

>>>>

\subsubsection{The Cancer Genome Atlas}
We obtained The Cancer Genome Atlas (TCGA) BRCA data as VCF files from the GDC data portal.
This data is in the category ``Simple Nucleotide Variation''.
After downloading, we use a custom script to name the samples in the files and filter for only the "Normal" tissue column.
We then use GATK to merge the files into a single VCF file.
